maASlin2

### 2019-12-03 scripts/26_unpack_pw.Rmd
unpacked

# the pantothenate (PWY-4242)
vb5 <- unpacked %>% 
  filter(str_detect(pw, '4242'))
```

>>>>

# the pantothenate (PWY-4242)

# get the top N results
N <- 20

vb5 <- unpacked %>% 
  filter(str_detect(pw, '4242')) %>% 
  filter(str_detect(pw, '\\|')) %>% 
  arrange(desc(cpm)) %>% 
  separate(pw, into = c('name','uniref90_ID'), '\\|') %>% 
  top_n(N)

vb5 %>% 
  ggbarplot(x = 'uniref90_ID', y = 'cpm', color = 'white', fill = 'forestgreen', title = 'PWY-4242')  +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggsave('../figs/unpack/PWY-4242.jpg', width = 8, height = 7, dpi = 300)

# COA 
unpacked %>% 
  filter(str_detect(pw, 'COA-PWY\\|')) %>% 
  filter(str_detect(pw, '\\|')) %>% 
  arrange(desc(cpm)) %>% 
  separate(pw, into = c('name','uniref90_ID'), '\\|') %>% 
  top_n(N) %>% 
  ggbarplot(x = 'uniref90_ID', y = 'cpm', color = 'white', fill = 'forestgreen', title = 'COA-PWY')  +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggsave('../figs/unpack/COA-PWY.jpg', width = 8, height = 7, dpi = 300)

# PANTOSYN-PWY
unpacked %>% 
  filter(str_detect(pw, 'PANTOSYN-PWY\\|')) %>% 
  filter(str_detect(pw, '\\|')) %>% 
  arrange(desc(cpm)) %>% 
  separate(pw, into = c('name','uniref90_ID'), '\\|') %>% 
  top_n(N) %>% 
  ggbarplot(x = 'uniref90_ID', y = 'cpm', color = 'white', fill = 'forestgreen', title = 'PANTOSYN-PWY')  +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggsave('../figs/unpack/PANTOSYN-PWY.jpg', width = 8, height = 7, dpi = 300)
```

### 2019-12-03 scripts/27_maASlin2.Rmd
unpacked

fit_data <- Maaslin2(
    pw, pheno, '../data/maASlin2/output',normalization  = 'NONE', transform = "LOG",  cores = 4, plot_heatmap = F,
    standardize = FALSE)
```

>>>>

fit_data <- Maaslin2(
    pw, pheno, '../data/maASlin2/output', normalization  = 'NONE', transform = "LOG",  cores = 4, plot_heatmap = F,
    standardize = FALSE)
```
